Improving Dynamic Kidney Exchange

### 2018-04-04 legacy/paper.tex
etc

\paragraph{Main idea} We study new dynamic kidney matching algorithm that takes as input a pool of patient-donor pairs and computes, for each cycle that is currently available for matching, a probability that it should be chosen to be cleared today, as well as another probability indicating whether we should not match any more cycles. In order to get these probabilities, our algorithm first produces a prior distribution estimated by observing past choices made by an infeasible optimal algorithm, and then updates these priors with simulations.

@@

\section{Acknowledgements}

This work was supported in part by Health Resources and Services Administration contract 234-2005-37011C. The content is the responsibility of the authors alone and does not necessarily reflect the views or policies of the Department of Health and Human Services, nor does mention of trade names, commercial products, or organizations imply endorsement by the U.S. Government.

>>>>

\paragraph{Main idea} We study a new dynamic kidney matching algorithm that takes as input a pool of patient-donor pairs and computes, for each cycle that is currently available for matching, a probability that it should be chosen to be cleared today, as well as another probability indicating whether we should not match any more cycles. In order to get these probabilities, our algorithm first produces a prior distribution estimated by observing past choices made by an infeasible optimal algorithm, and then updates these priors with simulations.

@@
